{{< var titll >}}

### 2024-08-17 index.qmd
break

# Testing (latest from Ed's Youtube stream)

## Installling packages

>>>>

```{webr-r}
#| echo: fenced
#| eval: true
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMP)
data(package='ManifoldDestinyWASMD')
```

```{r, echo=F}
suppressMessages(ManifoldDestiny::wasmconload()) 
apps <- appn0
adat <- apps[[1]]
amet <- apps[[2]]
cob <- Countinggraphs(adat,selvar=names(adat))
sum(dplyr::select(cob$rdfci,S,T,U,V))
cob$purging(z=amet$prg$z,pri=1) 
cob$plext(2)
sum(dplyr::select(cob$rdfce,S,T,U,V))
def <- Estimation(cob$rdfce)
def$regression("alpha=k0 + k1*g + k2*h")
summary(def$regsum[[1]])
```

```{r}
def$regression("alpha=k0 + k1*g + k2*h")
summary(def$regsum[[1]])
```

```{r}
def$regression("alpha=k0 + k1*g + k2*h + k3*g**2 + k4*h**2 + k5*g*h + k6*h**3 + k7*g*h + k8*g**2*h + k9*g*h**2")
summary(def$regsum[[1]])
```
